Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-14 Tex/Old text/chapters/chapter02.tex
thesis update

\begin{itemize}
\item Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
\item Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
\item Back-end: supports SAT and SMT solvers to discharge verification conditions.
\end{itemize}

@@

\begin{itemize}
\item A front-end that can read and compile C code, where the system's formal specification is first handled; 
\item Preprocessing steps deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally 
\item The SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability.
\end{itemize}

>>>>

\begin{itemize}
\item Front-end: scans, parses and type-checks C code; it converts control flow elements, such as \textit{if} or \textit{switch} statements, loops and jumps, into equivalent guarded \textit{goto} statements, thus aiming to reduce verification effort; 
\item Middle-end: performs symbolic execution by eagerly unwinding loops up to a fixed bound, which can be specified by the user on a per-loop basis or globally, for all loops and finally; 
\item Back-end: supports SAT and SMT solvers to discharge verification conditions (VCs).
\end{itemize}

@@

\begin{itemize}
\item A front-end that can read and compile C code, where the system's formal specification is first handled; 
\item Preprocessing steps deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally 
\item The SMT solving stage, where all constraints (C) and properties (P) of the system are encoded into SMT and checked for satisfiability ($C \wedge \neg P$).
\end{itemize}

### 2020-02-14 Tex/Old text/chapters/chapteroptimization.tex
thesis update

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
  \STATE Initialize variables \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
  \FOR {$HintCost=MinCost$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{mref}))$ \\
	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

@@

>>>>

 \begin{algorithm}
 \caption{Synthesis algorithm}
 \begin{algorithmic}[1]
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \REQUIRE weather data (temperature, solar irradiance); list of PV panels, controllers, batteries, and inverters datasheet information and cost; design requirements (load curve, peak demand, load surge power, daily energy consumption, battery autonomy, AC voltage); design assumptions (battery state of charge, depth of discharge, criteria and objectives for technical and cost analysis)
 \ENSURE FAIL (SAT) with counterexample showing the optimal sizing; SUCCESS (UNSAT), saying that the project has no feasible solution considering the requirements and the list of equipment
  \STATE Initialize variables \\
  \STATE Declare the maximum possible cost $MaxCost$  \\
  \STATE Calculate min possible Cost $MinCost$, based on the equipment list \\
  \FOR {$HintCost=MinCost$ to $MaxCost$}
 	\STATE Declare non-deterministic variable to select PV Panel from list \\
 	\STATE Declare non-deterministic variable to select Controller from list \\
 	\STATE Declare non-deterministic variable to select Battery from list \\
 	\STATE Declare non-deterministic variable to select Inverter from list \\ 	
 	\STATE Calculate $E_{corrected}, \, P_{min,panels} $ \\
	\STATE Calculate and define PV panels arrangement $N_{TP}, \, N_{PS}, N_{PP} $ \\
	\STATE Requirement enforced by \textbf{assume}$(P_{min,panels} \leq (N_{PS} \times N_{PP} \times P_{m,ref}))$ \\
	\STATE Calculate $I_{c,min} = N_{PP} \times I_{m,ref}$ \\
	\STATE Calculate $V_{c,min} = N_{PS} \times V_{m,ref}$ \\
 	\STATE Calculate $C_{bank}$ and $E_{b}$ \\
	\STATE Calculate and define battery arrangement $N_{BS}, \, N_{BP}, \, N_{BTotal}$ \\
	\STATE Requirement enforced by \textbf{assume} $(I_{min,DCbus} \leq (N_{BP} \times Capacity))$ \\
 	\STATE Controller requirements enforced by \textbf{assume}$((P_{controller} \geq P_{inverter}) \wedge V_{c} \wedge I_{c})$ \\
	\STATE Inverter requirements enforced by \textbf{assume}$(V_{in}DC \wedge V_{out}AC \wedge Demand \wedge P_{surge})$ \\
	\STATE non-deterministic variables hold feasible equipment and cost  \\
	\STATE $F_{obj} \leftarrow  N_{TP}*Panel_{Cost} \, + \, N_{TB}*Battery_{Cost} \, + Controller_{Cost} \, + \, Inverter_{Cost} \, + \, Installation_{Cost} \, + \, batrep_{Cost} \, + \, PWO\&M_{Cost}$ \\
	\STATE Violation check with \textbf{assert}$(F_{obj} > HintCost)$ \\
  \ENDFOR
 \RETURN $(\,)$ 
 \end{algorithmic} 
 \label{alg:opt-algorithm}
 \end{algorithm}

@@

The Algorithm~\ref{alg:opt-algorithm} is transformed by the verification engines into the Boolean expressions that are passed to the solver in order to verified ($C \wedge \neg P$). The quantifier-free formulae $C$ and $P$ are shown in Eq.~\ref{eq:quant_free_formulae_c} and Eq.~\ref{eq:quant_free_formulae_p}, respectively. Where $nd\_uchar$ denotes a non-deterministic unsigned char value. The conditional expression $ite(f,t_1,t_2)$ takes a Boolean formula $f$ and depending on its value selects either the second or the third argument. The function $select(a,i)$ denotes the value of $a$ at index position $i$. Worth to mention that it was removed from the representation all the bounds checks for arrays and matrices, and the division by zero check. During the verification process, the arithmetic operators induce checks to ensure that the arithmetic operations do not overflow and/ or underflow.

\begin{equation}
\label{eq:quant_free_formulae_c}
\begin{scriptsize}
C := \left [ \begin{array}{ll} 
	panelchoice = nd\_uchar \\
	\wedge \, \, batterychoice = nd\_uchar \\
	\wedge \, \, controllerchoice = nd\_uchar \\
	\wedge \, \, inverterchoice = nd\_uchar \\
	\wedge \, \, P_{m,ref} = select \, (PanelData \, [panelchoice][8]) \\
	\wedge \, \, I_{m,ref} = select \, (PanelData \, [panelchoice][9]) \\
	\wedge \, \, V_{m,ref} = select \, (PanelData \, [panelchoice][10]) \\
	\wedge \, \, Panel_{Cost} = select \, (PanelData \, [panelchoice][12]) \\
	\wedge \, \, \eta_{b} = select \, (BatteryData \, [batterychoice][0]) \\
	\wedge \, \, Vbat = select \, (BatteryData \, [batterychoice][1]) \\
	\wedge \, \, Capacity = select \, (BatteryData \, [batterychoice][2]) \\
	\wedge \, \, Battery_{Cost} = select \, (BatteryData \, [batterychoice][5]) \\
	\wedge \, \, \eta_{c} = select \, (ControllerData \, [controllerchoice][0]) \\
	\wedge \, \, I_{c} = select \, (ControllerData \, [controllerchoice][1]) \\
	\wedge \, \, V_{c,max} = select \, (ControllerData \, [controllerchoice][4]) \\
	\wedge \, \, Controller_{Cost} = select \, (ControllerData \, [controllerchoice][5]) \\
	\wedge \, \, \eta_{i} = select \, (InverterData \, [inverterchoice][0]) \\
	\wedge \, \, V_{in,DC} = select \, (InverterData \, [inverterchoice][1]) \\
	\wedge \, \, V_{out,AC} = select \, (InverterData \, [inverterchoice][2]) \\
	\wedge \, \, P_{AC,ref} = select \, (InverterData \, [inverterchoice][3]) \\
	\wedge \, \, MAX_{AC,ref} = select \, (InverterData \, [inverterchoice][4]) \\
	\wedge \, \, Inverter_{Cost} = select \, (InverterData \, [inverterchoice][5]) \\
	\wedge \, \, E_{corrected} = E_{consumption} / (\eta_{b} \times \eta_{c} \times \eta_{i}) \\
	\wedge \, \, P_{min,panels} = 1.25 \times E_{corrected} / Insolation \\
	\wedge \, \, N_{Pmin} = (int)(P_{min,panels} -1) / P{m,ref} + 1 \\
	\wedge \, \, N_{PP} = 2 \\
	\wedge \, \, N_{PS} = ite ( ((N_{Pmin} \% 2) == 0), (N_{Pmin}/2), ((N_{Pmin}+1) / 2) ) \\
	\wedge \, \, N_{TP} = N_{PP} \times N_{PS} \\
	\wedge \, \, I_{total,PVpanels} = 2 \times I_{m,ref} \\
	\wedge \, \, V_{total,PVpanels} = N_{PS} \times V_{m,ref} \\
	\wedge \, \, DOD_{max} = (100-SOC_{min}) \times 2 \\
	\wedge \, \, E_{b} = (autonomy/24) \times E_{corrected} \times 100/ DOD_{max} \\
	\wedge \, \, I_{min,DCbus} = E_{b}/(float)V_{system} \\
	\wedge \, \, N_{BS} = 24 / Vbat \\
	\wedge \, \, N_{BP} = ((I_{min,DCbus} - 1) / Capacity + 1) \\
	\wedge \, \, N_{Btotal} = N_{BS} \times N_{BP} \\
	\wedge \, \, F_{obj} = N_{TP} \times Panel_{Cost} + N_{Btotal} \times Battery_{Cost} + Controller_{Cost} + Inverter_{Cost} + O\&M_{Cost} + Inst_{Cost} \\
              \end{array} \right ]  \\ 
\end{scriptsize}
\end{equation}

\begin{equation}              
\label{eq:quant_free_formulae_p}
\begin{scriptsize}
P := \left [ \begin{array}{ll} 
	((panelchoice \geq 0) \, \, \wedge \, \, (panelchoice \leq 9)) \\
	\wedge \, \, ((batterychoice \geq 0) \, \, \wedge \, \, (batterychoice \leq 9)) \\
	\wedge \, \, ((controllerchoice \geq 0) \, \, \wedge \, \, (controllerchoice \leq 9)) \\
	\wedge \, \, ((inverterchoice \geq 0) \, \, \wedge \, \, (inverterchoice \leq 9)) \\
	\wedge \, \, (I_{c} \geq I_{total,PVpanels}) \\
	\wedge \, \, (V_{c,max} \geq V_{total,PVpanels}) \\
	\wedge \, \, ((V_{c,max} \times I_{C} \times \eta_{c}) \geq P_{AC,ref}) \\
	\wedge \, \, (V_{in,DC} \geq 24)  \\
	\wedge \, \, ((V_{out,AC} \geq OutletVoltage-10\%) \, \, \wedge \, \, (V_{out,AC} <= OutletVoltage+10\%)) \\
	\wedge \, \, ((MaximumLoadPower \leq P_{AC,ref}) \, \, \wedge \, \, (SurgeLoadPower \leq MAX_{AC,ref})) \\
	\wedge \, \, (F_{ob} > Value_{Iterative,optimal}) \\
              \end{array} \right ]  \\
\end{scriptsize}
\end{equation}
